\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-08 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	new file:   analysis/robustness_check.do 	deleted:    archive/.archieved.do 	deleted:    archive/RD design archived.Rmd 	deleted:    archive/analysis-2.do 	deleted:    archive/analysis.do 	deleted:    archive/analysis_1km.do 	deleted:    archive/clean_1km.do 	deleted:    archive/final_analysis.do 	deleted:    archive/quantile-regression.R 	deleted:    archive/quickly_filter_good_result.do 	deleted:    archive/some archived words.tex 	deleted:    archive/working on district level original.do 	deleted:    archive/working

Moreover, the overall market influence of real estate intermediaries is multifaceted. Utilizing a model predicated on perfect competition, \citet{williams_agency_1998} illustrates that excessive entry of brokers into the market can surpass the optimal allocation, thereby reducing social welfare. This is corroborated by studies indicating that an increase in the number of brokers can depress house prices and shorten transaction cycles \citep{https://doi.org/10.1002/jae.2891}. Additionally, \citet{qu_identifying_2021} highlights the moderating role of broker commissions in disseminating information during transactions, facilitating more efficient home sales. Other related literature includes \citep{doi:10.1080/10527001.2021.2016340, doi:10.1080/10835547.1996.12090852}.

@@

@@

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{Robustness Check By HHI Index}
    \label{tab:dynamic_hhi}
    \input{../result_tables/robust_hhi.tex}

>>>>

Moreover, the overall market influence of real estate intermediaries is multifaceted. Utilizing a model predicated on perfect competition, \citet{williams_agency_1998} illustrates that excessive entry of brokers into the market can surpass the optimal allocation, thereby reducing social welfare. This is corroborated by studies indicating that an increase in the number of brokers can depress house prices and shorten transaction cycles \citep{https://doi.org/10.1002/jae.2891}. Additionally, \citet{qu_identifying_2021} highlights the moderating role of broker commissions in disseminating information during transactions, facilitating more efficient home sales. Lastly, \citet{AGARWAL2024103668} utilized second-hand real estate transaction data from Beijing to demonstrate that real estate agents may significantly contribute to the formation of Yin-Yang contracts. They quantified the magnitude of the resulting tax evasion, attributing it to the learning-by-doing effect and peer influence among agents. However, their study lacked a spatial analysis component that would consider the local network effects. Other related literature includes \citep{doi:10.1080/10527001.2021.2016340, d082a2db-5cce-33f2-87c4-9cb020cc6666, doi:10.1080/10835547.1996.12090852}.

@@

  \bibitem[Agarwal et al.(2024)]{AGARWAL2024103668}
Agarwal, S., Kuang, W., Wang, L., and Yang, Y. 2024. The role of agents in fraudulent activities: Evidence from the housing market in Beijing. \textit{Journal of Urban Economics}, 142, 103668.

@@
